An Algorithmic Introduction to Lagrangian Coherent Structures

### 2013-11-11 main.tex
Change Bickley jet figures from backward time strainlines to forward time stretchlines

The forward time LCS obtained are shown in Figure~\ref{f:bickley jet hyperbolic shear lcs forward} and the backward time LCS (i.e. with the flow timespan set to $t \in [4 L_x/U,0]$ are shown in Figure~\ref{f:bickley jet hyperbolic shear lcs backward}. In Figures~\ref{f:bickley jet hyperbolic shear lcs details forward} and~\ref{f:bickley jet hyperbolic shear lcs details backward} the same LCS are shown with details.

Forward time stretchlines are shown in Figure~\ref{f:bickley jet forward stretchlines} and backward time stretchlines are shown in Figure~\ref{f:bickley jet backward stretchlines}.

\begin{figure}
\begin{center}
% demo/bickley_jet/hyperbolic_shear_lcs.m, commit aaf20ed
\includegraphics[width=\textwidth]{graphics/bickley_jet/hyperbolic_shear_lcs_forward}
\end{center}
\caption{Bickley jet forward time shear (green) and hyperbolic (red) LCS.}
\label{f:bickley jet hyperbolic shear lcs forward}
\end{figure}

\begin{figure}
\begin{center}
% demo/bickley_jet/hyperbolic_shear_lcs.m, commit aaf20ed
\includegraphics[width=\textwidth]{graphics/bickley_jet/hyperbolic_shear_lcs_backward}
\end{center}
\caption{Bickley jet backward time shear (green) and hyperbolic (blue) LCS.}
\label{f:bickley jet hyperbolic shear lcs backward}
\end{figure}

\begin{figure}
\begin{center}
% demo/bickley_jet/hyperbolic_shear_lcs_details.m, commit 3331187
\includegraphics[width=\textwidth]{graphics/bickley_jet/hyperbolic_shear_lcs_details_forward}
\end{center}
\caption{Same LCS as in Figure~\ref{f:bickley jet hyperbolic shear lcs forward}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed shearlines with thick green curves are outermost shearlines, i.e. shear LCS. White dots indicate $\lambda_2$ local maximums used for strainline integration initial positions.}
\label{f:bickley jet hyperbolic shear lcs details forward}
\end{figure}

\begin{figure}
\begin{center}
% demo/bickley_jet/hyperbolic_shear_lcs_details.m, commit 3331187
\includegraphics[width=\textwidth]{graphics/bickley_jet/hyperbolic_shear_lcs_details_backward}
\end{center}
\caption{Same LCS as in Figure~\ref{f:bickley jet hyperbolic shear lcs backward}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed shearlines with thick green curves are outermost shearlines, i.e. shear LCS. White dots indicate $\lambda_2$ local maximums used for strainline integration initial positions.}
\label{f:bickley jet hyperbolic shear lcs details backward}
\end{figure}

\begin{figure}
\begin{center}
% demo/bickley_jet/stretchlines.m, commit fc52909
\includegraphics[width=\textwidth]{graphics/bickley_jet/stretchlines_forward}
\end{center}
\caption{Bickley jet forward time stretchlines.}
\label{f:bickley jet forward stretchlines}
\end{figure}

\begin{figure}
\begin{center}
% demo/bickley_jet/stretchlines.m, commit fc52909
\includegraphics[width=\textwidth]{graphics/bickley_jet/stretchlines_backward}
\end{center}
\caption{Bickley jet backward time stretchlines.}
\label{f:bickley jet backward stretchlines}
\end{figure}

@@

\begin{figure}
\begin{center}
% demo/ocean_dataset/hyperbolic_shear_lcs.m, commit 65fab59
\includegraphics[width=\textwidth]{graphics/ocean_dataset/hyperbolic_shear_lcs_forward}
\end{center}
\caption{Ocean dataset forward time shear (green) and hyperbolic (red) LCS.}
\label{f:ocean dataset hyperbolic shear lcs forward}
\end{figure}

\begin{figure}
\begin{center}
% demo/ocean_dataset/hyperbolic_shear_lcs.m, commit 65fab59
\includegraphics[width=\textwidth]{graphics/ocean_dataset/hyperbolic_shear_lcs_backward}
\end{center}
\caption{Ocean dataset backward time shear (green) and hyperbolic (blue) LCS.}
\label{f:ocean dataset hyperbolic shear lcs backward}
\end{figure}

\begin{figure}
\begin{center}
% demo/ocean_dataset/hyperbolic_shear_lcs_details.m, commit 65fab59
\includegraphics[width=\textwidth]{graphics/ocean_dataset/hyperbolic_shear_lcs_details_forward}
\end{center}
\caption{Same LCS as in Figure~\ref{f:ocean dataset hyperbolic shear lcs forward}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed shearlines with thick green curves are outermost shearlines, i.e. shear LCS. White dots indicate $\lambda_2$ local maximums used for strainline integration initial positions.}
\label{f:ocean dataset hyperbolic shear lcs details forward}
\end{figure}

\begin{figure}
\begin{center}
% demo/ocean_dataset/hyperbolic_shear_lcs_details.m, commit 65fab59
\includegraphics[width=\textwidth]{graphics/ocean_dataset/hyperbolic_shear_lcs_details_backward}
\end{center}
\caption{Same LCS as in Figure~\ref{f:ocean dataset hyperbolic shear lcs backward}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed shearlines with thick green curves are outermost shearlines, i.e. shear LCS. White dots indicate $\lambda_2$ local maximums used for strainline integration initial positions.}
\label{f:ocean dataset hyperbolic shear lcs details backward}
\end{figure}

>>>>

The forward time LCS obtained are shown in Figure~\ref{f:bickley jet hyperbolic shear lcs strainline} and the backward time LCS (i.e. with the flow timespan set to $t \in [4 L_x/U,0]$ are shown in Figure~\ref{f:bickley jet hyperbolic shear lcs stretchline}. In Figures~\ref{f:bickley jet hyperbolic shear lcs details forward} and~\ref{f:bickley jet hyperbolic shear lcs details backward} the same LCS are shown with details.

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/bickley_jet/hyperbolic_shear_lcs_strainline}
\end{center}
\caption{Bickley jet lambda-line (green) and strainline (red) LCS.}
\label{f:bickley jet hyperbolic shear lcs strainline}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/bickley_jet/hyperbolic_shear_lcs_stretchline}
\end{center}
\caption{Bickley jet backward time shear (green) and stretchline (blue) LCS.}
\label{f:bickley jet hyperbolic shear lcs stretchline}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/bickley_jet/hyperbolic_shear_lcs_details_strainline}
\end{center}
\caption{Same LCS as in Figure~\ref{f:bickley jet hyperbolic shear lcs forward}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed shearlines with thick green curves are outermost shearlines, i.e. shear LCS. White dots indicate $\lambda_2$ local maximums used for strainline integration initial positions.}
\label{f:bickley jet hyperbolic shear lcs details forward}
\end{figure}

\begin{figure}
\begin{center}
% demo/bickley_jet/hyperbolic_shear_lcs_details.m, commit 3331187
\includegraphics[width=\textwidth]{graphics/bickley_jet/hyperbolic_shear_lcs_details_stretchline}
\end{center}
\caption{Same LCS as in Figure~\ref{f:bickley jet hyperbolic shear lcs backward}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed shearlines with thick green curves are outermost shearlines, i.e. shear LCS. White dots indicate $\lambda_2$ local maximums used for strainline integration initial positions.}
\label{f:bickley jet hyperbolic shear lcs details backward}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/ocean_dataset/hyperbolic_shear_lcs_strainline}
\end{center}
\caption{Ocean dataset forward time shear (green) and hyperbolic (red) LCS.}
\label{f:ocean dataset hyperbolic shear lcs strainline}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/ocean_dataset/hyperbolic_shear_lcs_stretchline}
\end{center}
\caption{Ocean dataset backward time shear (green) and hyperbolic (blue) LCS.}
\label{f:ocean dataset hyperbolic shear lcs stretchline}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/ocean_dataset/hyperbolic_shear_lcs_details_strainline}
\end{center}
\caption{Same LCS as in Figure~\ref{f:ocean dataset hyperbolic shear lcs forward}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed shearlines with thick green curves are outermost shearlines, i.e. shear LCS. White dots indicate $\lambda_2$ local maximums used for strainline integration initial positions.}
\label{f:ocean dataset hyperbolic shear lcs details forward}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/ocean_dataset/hyperbolic_shear_lcs_details_stretchline}
\end{center}
\caption{Same LCS as in Figure~\ref{f:ocean dataset hyperbolic shear lcs backward}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed shearlines with thick green curves are outermost shearlines, i.e. shear LCS. White dots indicate $\lambda_2$ local maximums used for strainline integration initial positions.}
\label{f:ocean dataset hyperbolic shear lcs details backward}
\end{figure}
